\documentclass{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage[none]{hyphenat}
\usepackage{mathrsfs}
\parindent=0pt

\def\upint{\mathchoice%
    {\mkern13mu\overline{\vphantom{\intop}\mkern7mu}\mkern-20mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
  \int}
\def\lowint{\mkern3mu\underline{\vphantom{\intop}\mkern7mu}\mkern-10mu\int}

\begin{document}



\textbf{\Large Chapter I: Varieties} \\\\



\emph{Author: Meng-Gen Tsai} \\
\emph{Email: plover@gmail.com} \\\\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\textbf{Problem I.1.6.}
\emph{Any nonempty open subset of an irreducible topological space is dense and irreducible.
If $Y$ is a subset of a topological space $X$, which is irreducible in its induced topology,
then the closure $\overline{Y}$ is also irreducible.} \\

\emph{Proof.}
\begin{enumerate}
\item[(1)]
\emph{Show that any nonempty open subset of an irreducible topological space
is dense.}
It suffices to show that $U_1 \cap U_2 \neq \varnothing$ for any
nonempty open subsets of an irreducible topological space.
  \begin{align*}
  &\forall \text{ nonempty open sets } U_1 \text{ and } U_2,
  U_1 \cap U_2 \neq \varnothing \\
  \Longleftrightarrow&
  \forall \text{ nonempty open sets } U_1 \text{ and } U_2,
  X - (U_1 \cap U_2) \neq X \\
  \Longleftrightarrow&
  \forall \text{ nonempty open sets } U_1 \text{ and } U_2,
  (X - U_1) \cup (X - U_2) \neq X \\
  \Longleftrightarrow&
  \forall \text{ proper closed sets } Y_1 \text{ and } Y_2,
  Y_1 \cup Y_2 \neq X \\
  \Longleftrightarrow&
  \nexists \text{ proper closed sets } Y_1 \text{ and } Y_2,
  Y_1 \cup Y_2 = X.
  \end{align*}
\item[(2)]
\emph{Show that any nonempty open subset of an irreducible topological space
is irreducible.}
Given any open subset $U$ of an irreducible topological space $X$.
Write $U \subseteq Y_1 \cup Y_2$ where $Y_1$ and $Y_2$ are closed in $X$.
  \begin{align*}
  U \subseteq Y_1 \cup Y_2
  \Longrightarrow&
  \overline{U} \subseteq \overline{Y_1 \cup Y_2} \\
  \Longrightarrow&
  X \subseteq Y_1 \cup Y_2
    &\text{($U$ is dense, $Y_1 \cup Y_2$ is closed)} \\
  \Longrightarrow&
  Y_1 = X \supseteq U \text{ or } Y_2 = X \supseteq U
    &\text{($X$ is irreducible)} \\
  \Longrightarrow&
  \text{$U$ is irreducible.}
  \end{align*}
\item[(3)]
\emph{Show that if $Y$ is a subset of a topological space $X$,
which is irreducible (in its induced topology),
then the closure $\overline{Y}$ is also irreducible.}
(Reductio ad absurdum)
If $\overline{Y}$ were reducible, there are two closed set $Y_1$ and $Y_2$
such that
$$\overline{Y} \subseteq Y_1 \cup Y_2,
\overline{Y} \not\subseteq Y_i (i = 1, 2).$$
  \begin{enumerate}
  \item[(a)]
  $Y \subseteq \overline{Y} \subseteq Y_1 \cup Y_2$.
  \item[(b)]
  $Y\not\subseteq Y_i (i = 1, 2)$. If not, $Y \subseteq Y_i$ for some $i$.
  Take closure to get $\overline{Y} \subseteq \overline{Y_i} = Y_i$ (since $Y_i$ is closed),
  contrary to the assumption.
  \end{enumerate}
  By (a)(b), $Y$ is reducible, which is absurd.
\end{enumerate}
$\Box$\\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{document}