\documentclass{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{mathrsfs}
\parindent=0pt

\def\upint{\mathchoice%
    {\mkern13mu\overline{\vphantom{\intop}\mkern7mu}\mkern-20mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
  \int}
\def\lowint{\mkern3mu\underline{\vphantom{\intop}\mkern7mu}\mkern-10mu\int}

\begin{document}

\textbf{\Large Chapter 3: Lebesgue Measure} \\\\



\emph{Author: Meng-Gen Tsai} \\
\emph{Email: plover@gmail.com} \\\\



\textbf{\large Section 3.1: Introduction} \\\\



\textbf{Problem 3.1.}
\emph{If $A$ and $B$ are two sets in $\mathfrak{M}$ with
$A \subseteq B$, then $mA \leq mB$.
This property is called monotonicity.} \\

\emph{Proof.}
Write
$$B
= B \cap X
= B \cap (A \cup \widetilde{A})
= (B \cap A) \cup (B \cap \widetilde{A})
= A \cup (B - A).$$
Here $B \cap A = A$ comes from $A \subseteq B$ (Problem 1.9).
Notice that $A$ and $B - A$ are disjoint.
Since $m$ is a countably additive measure ($m$ is nonnegative)
on a $\sigma$-algebra $\mathfrak{M}$,
$$mB = mA + m(B-A) \geq mA.$$
$\Box$ \\\\



\textbf{Problem 3.2.}
\emph{Let $\langle E_n \rangle$ be any sequence of sets in $\mathfrak{M}$.
Then $m(\bigcup E_n) \leq \sum mE_n$. (Hint: Use Proposition 1.2)
This property of a measure is called countable subadditivity.} \\

As the argument in Problem 3.1. \\

\emph{Proof.}
Since $\langle E_n \rangle$ is a sequence of sets in $\sigma$-algebra $\mathfrak{M}$,
by Proposition 1.2 and its proof,
there is a sequence $\langle F_n \rangle$ of sets in $\sigma$-algebra $\mathfrak{M}$
such that all $F_n$ are pairwise disjoint, $F_n \subseteq E_n$, and
$$\bigcup E_n = \bigcup F_n.$$
Since $m$ is a countably additive measure
on a $\sigma$-algebra $\mathfrak{M}$,
$$m\left( \bigcup E_n \right)
= m\left( \bigcup F_n \right)
= \sum mF_n
\geq \sum mE_n.$$
The last inequality holds by applying Exercise 3.1 on $F_n \subseteq E_n$ for any $n$.
$\Box$ \\\\



\textbf{Problem 3.3.}
\emph{If there is a set $A$ in $\mathfrak{M}$ such that $mA < \infty$,
then $m\varnothing = 0$.} \\

\emph{Proof.}
For such $A$, write $A = A \cup \varnothing$.
$A$ and $\varnothing$ are disjoint.
Since $m$ is a countably additive measure
on a $\sigma$-algebra $\mathfrak{M}$,
$$mA = mA + m\varnothing.$$
Since $mA < \infty$,
we can cancel out $mA$ on the both sides to get
$m\varnothing = 0$.
$\Box$ \\\\



\textbf{\large Section 3.2: Outer Measure} \\\\



\textbf{Problem 3.5.}
\emph{Let $A$ be the set of rational numbers between $0$ and $1$, and
let $\{ I_n\}$ be a finite collection of open intervals covering $A$.
Then $\sum l(I_n) \geq 1$.} \\

\emph{Idea.}
If $\{ I_n\}$ is a covering of $[0, 1]$ then we are done
since the length of $[0, 1]$ is $1$.
However, $\{ I_n\}$ only covers $A$ and not necessarily covers $[0, 1]$.
(For example,
$\{ I_n\}
= \left\{
\left( -89, \frac{1}{\sqrt{2}} \right),
\left( \frac{1}{\sqrt{2}}, 64 \right)
\right\}$ covers $A$ but not $\frac{1}{\sqrt{2}}$.)
Hence, it is natural to consider the closure of $A$ and
the closure of $I_n$.
Now $\{ \overline{I_n} \}$ is a (closed) covering of
$\overline{A} = [0, 1]$. \\

\emph{Proof.}
\begin{align*}
1
&= m^{*}[0, 1]
  &\text{(Proposition 3.1)} \\
&= m^{*}\overline{A}
  &\text{($A$ is dense in $[0, 1]$)} \\
&\leq m^{*}\left( \overline{\bigcup I_n} \right)
  &\text{(Proposition 2.10)} \\
&= m^{*}\left( \bigcup \overline{I_n} \right)
  &\text{(Proposition 2.10)} \\
&\leq \sum m^{*}(\overline{I_n})
  &\text{(Proposition 3.2)} \\
&= \sum l(\overline{I_n})
  &\text{(Proposition 3.1)} \\
&= \sum l(I_n)
  &\text{(definition of length)}
\end{align*}
$\Box$ \\\\



\textbf{Problem 3.6.}
\emph{Prove Proposition 5:
Given any set $A$ and any $\epsilon > 0$,
there is an open set $O$ such that $A \subseteq O$
and $m^{*}O \leq m^{*}A + \epsilon$.
There is a $G \in G_{\delta}$ such that $m^{*}G = m^{*}A$.} \\

\emph{Proof.}
\begin{enumerate}
\item[(1)]
\emph{Use the definition of the outer measure.}
By the definition of $m^{*}$,
for such $\epsilon > 0$ there exists a countable collection
$\{ I_n \}$ of open intervals that covers $A$ and
$$m^{*} A + \epsilon \geq \sum l(I_n).$$
\item[(2)]
\emph{Construct an open set $O$.}
Let $O = \bigcup I_n \supseteq A$
which is the union of any collection of open sets $I_n$.
By Proposition 2.7, $O$ is open.
\item[(3)]
\emph{Show that $m^{*}O \leq m^{*}A + \epsilon$.}
By Proposition 3.2 and 3.1,
$$m^{*}O
= m^{*} \left( \bigcup I_n \right)
\leq \sum m^{*} I_n
= \sum l(I_n)
\leq m^{*} A + \epsilon.$$
\end{enumerate}
Therefore, given any set $A$ and any $\epsilon > 0$,
there is an open set $O$ such that $A \subseteq O$
and $m^{*}O \leq m^{*}A + \epsilon$.

\begin{enumerate}
\item[(4)]
\emph{Construct $G \in G_{\delta}$ in a natural way.}
Given any $n \in \mathbb{N}$, there exists an open set $O_n$
such that $O_n \supseteq A$ and $m^{*}O_n \leq m^{*}A + \frac{1}{n}$.
Let
$$G = \bigcap_{n=1}^{\infty} O_n \in G_{\delta}.$$
\item[(5)]
\emph{Show that $m^{*}G = m^{*}A$.}
  \begin{enumerate}
  \item[(a)]
  Since $A \subseteq O_n$ for any $n \in \mathbb{N}$,
  $A \subseteq \bigcap_{n=1}^{\infty} O_n = G$.
  Thus $m^{*}A \leq m^{*}G$.
  \item[(b)]
  Since $O_n \supseteq \bigcap_{n=1}^{\infty} O_n = G$ for any $n \in \mathbb{N}$,
  $$m^{*}A + \frac{1}{n} \geq m^{*}O_n \geq m^{*}G$$
  for any $n \in \mathbb{N}$.
  Since $n \in \mathbb{N}$ is arbitrary, $m^{*}A \geq m^{*}G$.
  \end{enumerate}
By (a)(b), $m^{*}A = m^{*}G$.
\end{enumerate}
$\Box$ \\\\



\textbf{Problem 3.7.}
\emph{Prove that $m^{*}$ is translation invariant.} \\

\emph{Proof.}
Given $E \in \mathfrak{M}$ and $y \in \mathbb{R}$.
\begin{enumerate}
\item[(1)]
$m^{*}(E + y) \leq m^{*}E$.
Let $\{ I_n \}$ of open intervals that cover $E$.
Then $\{ I_n+y \}$ of open intervals that cover $E+y$.
Notice that the definition of $m^{*}$ and $l(I_n+y) = l(I_n)$, then
$$m^{*}(E + y) \leq \sum l(I_n+y) = \sum l(I_n).$$
Take the infimum of all such sum $\sum l(I_n)$,
$m^{*}(E + y) \leq m^{*}E$.
\item[(2)]
$m^{*}(E) \leq m^{*}(E + y)$.
Similar to (1).
\end{enumerate}
By (1)(2), $m^{*}(E + y) = m^{*}E$, that is, $m^{*}$ is translation invariant.
$\Box$ \\\\



\textbf{Problem 3.8.}
\emph{Prove that if $m^{*}A = 0$, then $m^{*}(A \cup B) = m^{*}B$.} \\

\emph{Proof.}
\begin{enumerate}
\item[(1)]
$m^{*}(A \cup B) \geq m^{*}B$ since $A \cup B \supseteq B$
and the definition of $m^{*}$.
(Any covering of $A \cup B$ by open intervals is also a covering of $B$
so that the latter infimum is taken over a larger collection than the former.)
\item[(2)]
$m^{*}(A \cup B) \leq m^{*}B$.
By Proposition 3.2,
$$m^{*}(A \cup B) \leq m^{*}A + m^{*}B = 0 + m^{*}B = m^{*}B.$$
\end{enumerate}
By (1)(2), $m^{*}(A \cup B) = m^{*}B$.
$\Box$ \\\\



\end{document}