\documentclass{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{mathrsfs}
\parindent=0pt

\def\upint{\mathchoice%
    {\mkern13mu\overline{\vphantom{\intop}\mkern7mu}\mkern-20mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
    {\mkern7mu\overline{\vphantom{\intop}\mkern7mu}\mkern-14mu}%
  \int}
\def\lowint{\mkern3mu\underline{\vphantom{\intop}\mkern7mu}\mkern-10mu\int}

\begin{document}

\textbf{\Large Chapter 1: Rings and Ideals} \\\\



\emph{Author: Meng-Gen Tsai} \\
\emph{Email: plover@gmail.com} \\\\



% https://spaces.ac.cn/usr/uploads/2017/07/4208763092.pdf
% https://www.math.arizona.edu/~cais/371Page/homework/371s1.pdf



\textbf{Exercise 1.1}
\emph{Let $x$ be a nilpotent element of $A$.
Show that $1+x$ is a unit of $A$.
Deduce that the sum of a nilpotent element and a unit is a unit.} \\

\emph{Proof.}
\begin{enumerate}
\item[(1)]
Suppose $x^m = 0$ for some odd integer $m \geq 0$.
Then
$$1 = 1+x^m = (1+x)(1-x+x^2-\cdots+(-1)^{m-1}x^{m-1}),$$
or $1+x$ is a unit.
\item[(2)]
If $u$ is any unit and $x$ is any nilpotent,
$u + x= u \cdot (1 + u^{-1}x)$ is a product of two units
(using that $u^{-1}x$ is nilpotent and applying (1))
and hence a unit again.
\end{enumerate}
$\Box$ \\

\emph{Proof (Proposition 1.9).}
\begin{enumerate}
\item[(1)]
\emph{The nilradical is a subset of the Jacobson radical.}
\begin{enumerate}
\item[(a)]
The nilradical $\mathfrak{N}$ of $A$ is the intersection of all the prime ideals of $A$
by Proposition 1.8.
\item[(b)]
The Jacobson radical $\mathfrak{R}$ of $A$ is the intersection of all the maximal ideals of $A$
by definition.
\end{enumerate}
\item[(2)]
By Proposition 1.9,
$x \in \mathfrak{R}$ if and only if
$1-xy$ is a unit in $A$ for all $y \in A$.
So $1+x = 1 - (-x) \cdot 1$ is a unit in $A$
since $x$ is a nilpotent and $\mathfrak{R}$ is an ideal.
\end{enumerate}
$\Box$ \\\\



\textbf{Exercise 1.2}
\emph{Let $A$ be a ring and
let $A[x]$ be the ring of polynomials in an indeterminate $x$,
with coefficients in $A$.
Let $f = a_0 + a_1 x + \cdots + a_n x^n \in A[x]$.
Prove that}
\begin{enumerate}
\item[(i)]
\emph{$f$ is a unit in $A[x]$ if and only if
$a_0$ is a unit in $A$ and
$a_1, ..., a_n$ are nilpotent.
(Hint: If $b_0 + b_1 x + \cdots + b_m x^m$ is the inverse of $f$,
prove by induction on $r$ that $a_n^{r+1} b_{m-r} = 0$.
Hence show that $a_n$ is nilpotent, and then use Exercise 1.1.)}
\item[(ii)]
\emph{$f$ is nilpotent if and only if
$a_0, a_1, ..., a_n$ are nilpotent.}
\item[(iii)]
\emph{$f$ is a zero-divisor if and only if
there exists $a \neq 0$ such that $af = 0$.
(Hint: Choose a polynomial $g = b_0 + b_1 x + \cdots + b_m x^m$
of least degree $m$ such that $fg = 0$.
Then $a_n b_m = 0$, hence $a_n g = 0$
(because $a_n g$ annihilates $f$ and has degree $< m$).
Now show by induction that $a_{n-r}g = 0$ $(0 \leq r \leq n)$.)}
\item[(iv)]
\emph{$f$ is said to be primitive if $(a_0, a_1, ..., a_n) = (1)$.
Prove that if $f, g \in A[x]$, then $fg$ is primitive if and only if
$f$ and $g$ are primitive.} \\
\end{enumerate}

\emph{Proof of (i).}
\begin{enumerate}
\item[(1)]
$(\Longleftarrow)$ holds by Exercise 1.1.
\item[(2)]
$(\Longrightarrow)$
There exists the inverse $g$ of $f$, say $g = b_0 + b_1 x + \cdots + b_m x^m$
satisfying
$1 = fg$.
Clearly, $1 = a_0 b_0$, or $a_0$ is a unit in $A$.
Also,
\begin{align*}
0
&= a_n b_m, \\
0
&= a_n b_{m-1} + a_{n-1} b_m, \\
0
&= a_n b_{m-2} + a_{n-1} b_{m-1} + a_{n-2} b_m, \\
& \cdots
\end{align*}
A direct computing shows that
\begin{align*}
0
&= a_n^{1} b_m, \\
0
&= a_n (a_n b_{m-1} + a_{n-1} b_m) \\
&= a_n^{2} b_{m-1} + a_{n-1} a_n b_m \\
&= a_n^{2} b_{m-1}, \\
0
&= a_n^{2} (a_n b_{m-2} + a_{n-1} b_{m-1} + a_{n-2} b_m) \\
&= a_n^{3} b_{m-2} + a_{n-1} a_n^{2} b_{m-1} + a_{n-2} a_n^{2} b_m \\
&= a_n^{3} b_{m-2}, \\
& \cdots
\end{align*}
So we might have $a_n^{r+1} b_{m-r} = 0$ for $r = 0, 1, 2, ..., m$.
\item[(3)]
\emph{Show that $a_n^{r+1} b_{m-r} = 0$ for $r = 0, 1, 2, ..., m$
by induction on $r$.}
\begin{enumerate}
\item[(a)]
As $r = 0$, $a_n b_m = 0$ by comparing the coefficient of $fg = 1$ at $x^{n+m}$.
\item[(b)]
For any $r > 0$, comparing the coefficient of $fg = 1$ at $x^{n+m-r}$,
$$0 = a_n b_{m-r} + a_{n-1} b_{m-r+1} + \cdots + a_{n-r} b_m.$$
Multiplying by $a_n^r$ on the both sides,
\begin{align*}
0
&= a_n^{r+1} b_{m-r} + a_{n-1} a_n^{r} b_{m-r+1} + \cdots + a_{n-r} a_n^{r} b_m \\
&= a_n^{r+1} b_{m-r}.
\end{align*}
by the induction hypothesis.
\end{enumerate}
\item[(4)]
\emph{$a_n$ is a nilpotent.}
Putting $r = m$ in $a_n^{r+1} b_{m-r} = 0$ and get $a_n^{m+1} b_0 = 0$.
Notice that $b_0$ is a unit, $a_n^{m+1} = 0$, or $a_n$ is a nilpotent.
\item[(5)]
Consider $f - a_n x^n = a_0 + a_1 x + \cdots + a_{n-1} x^{n-1}$,
a polynomial $\in A[x]$ of degree $n-1$.
Note that $f$ is a unit and $a_n x^n$ is a nilpotent.
By Exercise 1.1, $f - a_n x^n$ is a unit too.
Applying the (2)(3)(4) again, $a_{n-1}$ is a nilpotent as $n-1 > 0$,
that is, applying descending induction on $n$ then yields the desired property.
\end{enumerate}
$\Box$ \\

\emph{Proof of (ii).}
\begin{enumerate}
\item[(1)]
$(\Longleftarrow)$ holds since the nilradical of any ring is an ideal.
\item[(2)]
$(\Longrightarrow)$ $f^N = 0$ for some $N > 0$.
So $0 = f^N = a_n^N x^{nN} + \cdots + a_0^N$.
Comparing the coefficient in the leading term $x^{nN}$ leads to $a_n^N = 0$,
or $a_n$ is a nilpotent.
\item[(3)]
Consider $f - a_n x^n = a_0 + a_1 x + \cdots + a_{n-1} x^{n-1}$,
a polynomial $\in A[x]$ of degree $n-1$.
Note that $f$ and $a_n x^n$ are nilpotents.
$f - a_n x^n$ is a nilpotent too.
Similar to step (5) in the proof of (i),
applying descending induction on $n$ then yields the desired property.
\end{enumerate}
$\Box$ \\

\emph{Proof of (iii).}
\begin{enumerate}
\item[(1)]
$(\Longleftarrow)$ holds trivially.
\item[(2)]
$(\Longrightarrow)$
Pick a polynomial $g = b_0 + b_1 x + \cdots + b_m x^m$
of least degree $m$ such that $fg = 0$.
Especially, $a_n b_m = 0$.
\item[(3)]
Consider
\begin{align*}
a_n g
&= a_n b_0 + \cdots + a_n b_{m-1} x^{m-1} + a_n b_m x^m \\
&= a_n b_0 + \cdots + a_n b_{m-1} x^{m-1}
\end{align*}
(since $a_n b_m = 0$).
$a_n g$ is a polynomial over $A$ of having degree strictly less than $m$.
Notice that $f \cdot (a_n g) = a_n \cdot (fg)= 0$.
By minimality of $m$, $a_n g = 0$.
\item[(4)]
Induction on the degree $n$ of $f$.
\begin{enumerate}
\item[(a)]
As $n = 0$, $f = a_0$. There exists $b_m \neq 0$ such that $b_m f = b_m a_0 = 0$ by (2).
\item[(b)]
For any zero-divisor $f$ of degree $n$,
there is a polynomial $g = b_0 + b_1 x + \cdots + b_m x^m$
of least degree $m$ such that $fg = 0$. By (2)(3),
\begin{align*}
(f - a_n x^n) \cdot g
&= fg - a_n x^n g \\
&= 0 - 0 \\
&= 0.
\end{align*}
That is, $f - a_n x^n$ is a zero-divisor of degree $n-1$.
By the induction hypothesis,
there exists $b_m \neq 0$ such that $b_{m}(f - a_n x^n) = 0$.
So $b_m f = b_{m}(f - a_n x^n) + b_m a_n x^n = 0 + 0 = 0$.
\item[(c)]
By (a)(b), $(\Longrightarrow)$ holds by mathematical induction.
\end{enumerate}
\end{enumerate}
$\Box$ \\

\emph{Proof of (iv).}
Note that
\begin{enumerate}
\item[(1)]
$f \notin \mathfrak{m}[x]$ for any maximal ideal $\mathfrak{m}$ of $A$
if and only if $f$ is primitive.
\item[(2)]
For any maximal ideal $\mathfrak{m}$ of $A$,
$A/\mathfrak{m}$ is a field (or an integral domain).
\item[(3)]
$A[x]$ is an integral domain if $A$ is an integral domain.
\item[(4)]
$A[x]/\mathfrak{m}[x] \cong (A/\mathfrak{m})[x]$ as a ring isomorphism.
\end{enumerate}
Hence,
\begin{align*}
f, g:\text{ primitive}
&\Longleftrightarrow
f, g \notin \mathfrak{m}[x] \text{ for any maximal ideal } \mathfrak{m} \\
&\Longleftrightarrow
f, g \neq 0 \text{ in } (A/\mathfrak{m})[x] \text{ for any maximal ideal } \mathfrak{m} \\
&\Longleftrightarrow
fg \neq 0 \text{ in } (A/\mathfrak{m})[x] \text{ for any maximal ideal } \mathfrak{m} \\
&\Longleftrightarrow
fg \notin \mathfrak{m}[x] \text{ for any maximal ideal } \mathfrak{m} \\
&\Longleftrightarrow
fg:\text{ primitive}.
\end{align*}
$\Box$ \\\\



\end{document}